ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-22 docs/paper/paper.tex
webapp image

@@

% https://www.overleaf.com/learn/latex/Inserting_Images
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{cover.png}
	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image, (D) prediction image}
	\label{fig:fig1}
\end{figure}

@@

Assets are digital representations of a 3D object. In the engineering and manufacturing world, assets are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}. In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}. Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the boundaries of an object. Vertices are connected by edges, and a closed loop creates a polygon known as a face. Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras. Finally, asset creation also encompasses teh process of material creation. The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.

@@

The datasets used by companies today are almost exclusively collected.

Data for ML systems is collected. Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.

A huge market for the selling and reselling of collected data has emerged, which presents an existential threat to privacy.

@@

@@

\subsection{User Interfaces}
\label{sec:cloudbackend}

We provide three different interfaces to interact with our product: an API, a CLI, and a graphical WebApp.

Power users want an API (application programming interface) and CLI (command line interface).

Building a ramp for the bulk of the developer community requires a GUI

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{workflow.png}
	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
	\label{fig:fig3}
\end{figure}

@@

See Figure \ref{fig:fig3}.

The full workflow for synthetic data can be reduced into four key steps:

\begin{itemize}
	\item \emph{Design}.
	\item \emph{Generation}.
	\item \emph{Evaluation}.
	\item \emph{Iteration}.
\end{itemize}

@@

Design the Sim

Sim is short for simulation.

A sim is controlled through a single run script, which has a single run() function

Relevant parameters are put as kwargs in the run() function, which allows configuration through gin config

Gin configuration allows for modular python library design

@@

Generate the dataset

@@

Cycles vs Eevee

@@

Evaluate the datasets

@@

Iterate

>>>>

\usepackage{xcolor}
\usepackage{listings}		% code
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

@@

% https://www.overleaf.com/learn/latex/Inserting_Images
\begin{figure}[!ht]
	\centering
	\includegraphics[width=\textwidth]{cover.png}
	\caption{Synthetic images of a raspberri pi created with zpy: (A) color image, (B) segmentation image, (C) depth image. These images are used to train a deep learning model, which predicts bounding boxes on key components as seen in the (D) prediction image}
	\label{fig:fig1}
\end{figure}

@@

Assets are digital representations of a 3D object. In the engineering and manufacturing world, assets are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}. In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}. Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the surface of an object. Vertices are connected by edges, and a closed loop creates a polygon known as a face. Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras. Finally, asset creation also encompasses the process of material creation. The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.

@@

The datasets used by companies today are almost exclusively collected. Images and annotations are gradually saved as they are generated by users of a product. Collecting a dataset large enough to train a robust machine learning model can take years.

Only companies that have the scale and have set up the infrastructure to collect and store large datasets will have the datasets required to train models.

In order to compete, small or newly formed companies often resort to purchasing data from a third party supplier. This market for the selling and reselling of collected data presents an existential threat to privacy. Though some regulations have emerged, famously GDPR in Europe, these have yet to change the landscape of the market for collected data.

@@

Given

@@

\subsection{User Interfaces}
\label{sec:userinterfaces}

We provide three different interfaces to interact with our product: a Python API \ref{lst:api}, a CLI \ref{lst:cli}, and a graphical WebApp \ref{fig:webapp}. Power users want an API (application programming interface) and CLI (command line interface). Building a ramp for the bulk of the developer community requires a GUI

\begin{lstlisting}[language=Python,caption={Generating a dataset using the zpy python API.},label={lst:api}]
import zpy
zpy.generate()
\end{lstlisting}

\begin{lstlisting}[language=bash,caption={Generating a dataset using the zpy CLI},label={lst:cli}]
# First you will need to log in and set the project (image generation gets billed according to project)
zpy login $USERNAME 
zpy project set $PROJECT_UUID

# Generate the dataset
zpy create dataset "redbull cans and packs" can_v6 num_images 1000
\end{lstlisting}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{webapp.png}
	\caption{A visual interface for synthetic data creation via a WebApp.}
	\label{fig:webapp}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{workflow.png}
	\caption{The Synthetic Data Workflow allows for iteration of the dataset.}
	\label{fig:workflow}
\end{figure}

@@

The full workflow for synthetic data can be reduced into four key steps: \emph{Design} \ref{sec:worflowdesign}, \emph{Generation} \ref{sec:generation}, \emph{Evaluation} \ref{sec:evaluation}, \emph{Iteration} \ref{sec:iteration}. The synthetic data workflow is similar to the workflow when using collected data, with the key exception that it allows for iteration on the dataset itself \ref{fig:workflow}.

@@

The first step in the syntehtic data workflow is to design and create the sim, short for simulation. A sim is a collection of assets controlled through a single script. The run() function in the script acts as the point of entry for any generation process. Relevant parameters are put as kwargs in the run() function, which allows configuration through gin-config, a python package for configuration of python libraries.

@@

@@

Datasets can be rendered locally directly inside the Blender GUI. This allows for easy debugging when developing a sim. Once it is working locally, a sim can be exported into a zip file which will contain all the asset dependencies required. This zip file can be uploaded to the cloud with any of the user interfaces described in \ref{sec:userinterfaces}.

Dataset are then generated in the cloud \ref{sec:cloudbackend}.

We provide workflows for packaging several smaller datasets into a single larger dataset, as well as sorting individual datapoints into test, train, and validation buckets.

@@

@@
